Active-contours driven registration of diffusion MR images of the brain

### 2015-03-16 Publications/2015-NeuroImage/05-results.tex
new violinplot for realdata

\begin{figure*}
	\includegraphics[width=\linewidth]{figures/figure05.pdf}
	\caption{The evaluation instrument automatically renders the overlay between the
	  target \gls*{fa} image and the resulting contours after distortion estimation (yellow color) and
	  their theoretical location using the ground-truth (green color).
	The first two rows show several axial slices for \emph{regseg} (``proposed'' row) and the
	  competing method.
	The last two rows represent the sagittal view.
	We intentionally omitted the coronal slicing as it is the least informative, given the directional property
	  of distortions.
	Red arrows point to regions where the accuracy of the proposed method more clearly overperformed
	  the competing method.
	\todo[inline]{This figure will also have the box-plots of the errors of surfaces for both regseg
	and the t2b method}
	}\label{fig:results_real}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tikzpicture}
        \node[inner sep=15pt, draw=black!40](fig05a) at (0,11)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure05-a}};
        \node[inner sep=15pt, draw=black!40](fig05b) at (0,0)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure05-b}};
        % \node[inner sep=5pt, draw=black!40](fig03c) at (0,0)
        %   {\includegraphics[width=\linewidth]{figures/figure03-c}};
        \node[circle, text=black!75] at (-9.5,17) {\Huge \textbf{A}};
        \node[circle, text=black!75] at (-9.5,3) {\Huge \textbf{B}};
        % \node[circle, text=black!75] at (-8.8,3.4) {\Huge \textbf{C}};
      \end{tikzpicture}
    }%
	\caption{The evaluation instrument automatically renders the overlay between the
	  target \gls*{fa} image and the resulting contours after distortion estimation (yellow color) and
	  their theoretical location using the ground-truth (green color).
	The first two rows show several axial slices for \emph{regseg} (``proposed'' row) and the
	  competing method.
	The last two rows represent the sagittal view.
	We intentionally omitted the coronal slicing as it is the least informative, given the directional property
	  of distortions.
	Red arrows point to regions where the accuracy of the proposed method more clearly overperformed
	  the competing method.
	}\label{fig:results_real}
\end{figure*}
